\documentclass{sstt-2026-abstract}
%% The class already loads standard commonly-used packages:
%% amsmath, hyperref, biblatex, tikz-cd, etc.
%%
%% To help us preparing a book of abstracts, please avoid loading further
%% packages unless absolutely essential.

\addbibresource{bibliography.bib}

%%%%%%%%%%%%%%%%
%% Extra commands, theorem types (\newtheorem), etc
%% Please keep simple and use sparingly

%%%%%%%%%%%%%%%%
%% Abstract metadata
%% These replace the usual \title, \author commands

\abstracttitle{Dimensional Information in a Type Theory with a Definitionally Proof Irrelevant Layer}

\abstractspeaker{Julien Marquet-Wagner}
\abstractcoauthor{Sophie d'Espalungue}

\begin{document}

%%%%%%%%%%%%%%%%
%% Abstract main text

\color{black} % Current

We report on an implementation of a dependent type theory that supports
definitional proof irrelevance. Our type theory is organized into two
interwoven layers labelled by dimensions $-1$ and $0$, so that every type and
every term is introduced at a specified dimension. This dimension determines
the status of equality between terms, as follows. Types of dimension~$-1$ are
definitionally proof-irrelevant, hence we name them propositions. Types of
dimension~$0$ have $-1$-dimensional equality types and we name them sets. All
our results are formalized in Agda \cite{Agda} and our sources are available
online\footnote{\url{https://github.com/thejohncrafter/SSTT26}}.

%%%%%%%%%%%%%%%%%%%

Contexts may contain both propositions and sets, letting the two layers
interact in a nontrivial way. We keep our type theory minimal, with only
Pi-types, universes, and equality, and explore the behavior of type formers
with respect the layers.

%%%%%%%%%%%%%%%%%%%

Our approach is close to that of relevance marks \cite{proofirrelwithoutk},
where relevance information is local at binders. We take a geometric point of
view and structure the syntax around the notion of dimension instead. This
allows us to state definitional proof irrelevance without referring to
universes: any two $-1$-dimensional terms of the same $-1$-dimensional type are
convertible.

%%%%%%%%%%%%%%%%%%%

Our implementation is derived from an implementation of a minimal type theory
relying on an extrinsically typed, intrinsically scoped inductive-inductive
syntax introduced by the first author \cite{IISyntax}. With this approach, the
dimensional information flows through the definitions almost always silently,
except where layer-specific behavior is involved.

%%%%%%%%%%%%%%%%
%% Bibliography, if needed:
\printbibliography

\end{document}
